\section{Inheriting Properties}

\begin{frame}
  \frametitle{JavaScript Does Property Inheritance Differently}
  \begin{itemize}
    \item Not class-based or "classical" inheritance.
    \item Prototypal inheritance.
  \end{itemize}
\end{frame}

\begin{frame}[fragile]
    \frametitle{Any Function Instance Can be Used as a Constructor}
    \begin{lstlisting}[language=JavaScript]
        var MyConstructor = function(x) {
          this.myProperty = x;
          // ...
        }
        var obj = new MyConstructor(5);
        console.log(obj);
            // ==> MyConstructor {myProperty: 5}
    \end{lstlisting}
\end{frame}

\begin{frame}
    \frametitle{Every Constructor Instance (i.e. Function Instance) has a
                \texttt{prototype} Property}
    \begin{itemize}
      \item{An object \texttt{o} constructed by some constructor \texttt{C} will
            inherit properties from \texttt{C.prototype} via a ``hidden''
            property \texttt{o.\_\_proto\_\_}.}
      \item{We can manually set \texttt{C.prototype}.}
      \item{By default, JS initializes the \texttt{protoype} to an empty object
            instance.}
    \end{itemize}
\end{frame}

\begin{frame}
    \frametitle{There are Actually Three Ways to Designate an Object's Prototype}
    \begin{itemize}
        \item{\textbf{Constructor Functions:} Set a constructor function's
              \texttt{prototype} property, and this object will become the
              prototype of all object instanted from this constructor. (We saw
              this one.)}
        \item{\textbf{Explictly at Object Instantiation:} The
              \texttt{Object.create()} helper function creates a new object
              instance with a given prototype.}
        \item{\textbf{Set Manually}}: \texttt{Object.setPrototypeOf()}
    \end{itemize}
\end{frame}

\begin{frame}
    \frametitle{Prototype Chain Search}
    \begin{itemize}
        \item{\textbf{Reading From obj.p:} The prototype chain of \texttt{obj}
              is searched, looking for the first object which \textit{defines}
              \texttt{p}. If \texttt{p} is never found, \texttt{undefined} is
              returned.}
        \item{\textbf{Assigning To obj.p:}} The prototype chain of \texttt{obj}
              is searched, looking for the first object which \textit{defines}
              \texttt{p}. If \texttt{p} is never found, \texttt{p} is defined
              directly on \texttt{obj}.
    \end{itemize}
\end{frame}

\begin{frame}
    \frametitle{Scope Chains vs Prototype Chains}
    \begin{itemize}
        \item{\textbf{Scope Chain:}}
        \begin{itemize}
            \item{Extended by function call.}
            \item{Extends from function definition scope. (Lexical/static
                  scoping)}
            \item{Stored values accessed via variable accesses.}
            \item{The chain's root is always the global object.}
        \end{itemize}
        \item{\textbf{Prototype Chain:}}
        \begin{itemize}
            \item{Extended by object creation.}
            \item{Extends from a designated object.}
            \item{Stored values accessed via property accesses.}
            \item{The chain's root is always \texttt{null}.}
        \end{itemize}
    \end{itemize}
\end{frame}
